The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-29 paper/ms.tex
first pass en la parte observacional

We use information from seven observational data sets.
Four obtained with the Hubble Space Telescope (HST) and three from
ground-based telescopes.
All of them select galaxy candidates at $z\sim 6$ using the drop-out
technique \citep{Steidel96}.

The data from the Hubble Space Telescope Legacy (HSTL)
\citep{Bouwens15} is a compilation  of observations taken with the
Advanced Camera for Surveys (ACS) and near-infrared Wide Field Camera
3 (WFC3/IR) since 2002 through 2012.

The information in that study comes from the ACS and WFC3/IR using the
filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
$J{125}$,  $JH_{140}$ and $H_{160}$.
The study inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.

The total survey area is $740.8$ arcmin$^2$ over five different lines
of sight, with a total estimated volume of  $1.8 \times 10^6
\textrm{Mpc}^3$ comoving. 
The limiting magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
$\sim30 $mag in  the  deepest field (XDF). 
The total number of $z=6$ LBG candidates is $940$, most of 
them in the faint end of the LF given the relativeley small survey volume.
The restframe UV magnitudes for these candidates are in the range.
$-22.52\leq M_{1600} \leq -16.77$.
\citet{Bouwens15} estimated the Luminosity Function (LF) using a 
stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
They obtained the following Schechter parameters:
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{Bouwens15} notes that only using few fields of view can yield a
LF with a deviations from the Schechter shape.

\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS 
fields, along with two of the Hubble Frontier Fields (HFF) of deep parallel 
observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 
clusters. 
The HFF uses the ACS and the WFC3/IR with the same filters
aforementioned except $z_{850}$.

The total survey area is around   $\sim300\textrm{arcmin}^2$ with a
total estimated volume of $8\times 10^5$ Mpc$^{-3}$.
There are 706 photometric candidates at redshift 6  defined as the
interval $5.5<z<6.5$. 
The Schechter function parameters estimated for this data set 
are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.

\citet{Willott13} presented the sixth release of the Canada-France-Hawaii 
Telescope Legacy Survey CFHTLS. The observations where performed over four 
separated fields covering a total area $\sim 4 \deg^2$ (a large area), it gives 
this survey great robustness. Optical observations used MegaCam  %%%%%%[CITE REQUIRED] 
with $u^* g' r' i' z'$ filters. The main selection criteria: all the 
objects must be brighter than magnitude $z' = 25.3$. The final 
number of LBGs founded was 40. Moreover, they get spectroscopic confirmation 
for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
has a $\ll 5.5$-square arcmin field of view, giving a volume 
$\sim 1.09 \times 10^7 \textrm{Mpc}^3$. 
They show incompleteness in the sample due to 
foreground contamination and the detection algorithm; there is no warranty to 
have every object brighter than the limit magnitude on the faint limit. The full 
galaxy LF at $z=6$ cannot be obtained as in other studies. Nevertheless, this 
survey was focussed on the highly luminous LBGs. LF is calculated using the 
stepwise maximum likelihood method of \citet{Efstathiou88}, within magnitudes 
from $M_{1350} = -22.5$ up to $-20.5$. The luminosity function of $z=5.9$ shows 
an exponential decline at the bright end, where feedback processes and 
inefficient last cooling limites star forming in bright galaxies hosted in the 
most massive halos.

\citet{McLure09} build the luminosity function for $z=5$ and $z=6$ using data 
from two ground-based telescopes: the United Kingdom Infrared Telescope in the 
near-IR imaging and Subaru Telescope for the optical imaging. They use the first 
data release of the UKIRT Infrared  DeepSky Survey Ultra Deep Survey (UDS), 
together with the Subaru XMM-Newton  Survey (SXDS). Total observed area is 
$0.63 \deg^2$ uniformly covered by booth catalogues.
The volume in this survey is $\sim 3 \times 10^6 \textrm{Mpc}^3$.
The UKIRT was equipped with the WFCAM using $J K$ filters. The Subaru was 
equipped with the Suprime-Cam with the $B V R i' z'$ filters. All candidates 
where brighter than $z'=26$. The UV rest frame magnitude range is 
$-22.4\leq M_{1500} \leq-20.6$. The LF was calculated using the maximum 
likelihood estimator of \citet{Schmidt68}. Their analysis gave a total number of 
104 LBG candidates in the redshift range $5.7\leq z \leq 6.3$. LF was 
parameterized according to the Schechter function with 
$\phi^* =(1.8\pm 0.5)\times 10 ^{-3} \textrm{Mpc}^{-3}$, 
$M^*_{1500} = -20.04\pm 0.12$ and $\alpha = -1.71 \pm 0.11$.

The dataset was retrieved from \cite{McLure09} graph using
GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.

@@

>>>>

We use information compiled in four different publications. 
All of them select galaxy candidates at $z\sim 6$ using the drop-out
technique \citep{Steidel96}.  
In what follows we describe the relevant details of each reference.

\subsection{Bouwens et al. 2015}
\citet{Bouwens15} presented results from a compilation of
observations taken with the Advanced Camera for Surveys (ACS) and
near-infrared Wide Field Camera 3 (WFC3/IR) since 2002 through 2012. 
The study inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS.
%The information in that study comes from the ACS and WFC3/IR using the
%filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
%$J{125}$,  $JH_{140}$ and $H_{160}$.

%with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
%60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.  
The total survey area is $740.8$ arcmin$^2$ over five different lines
of sight, with a total estimated volume of  $1.8 \times 10^6
\textrm{Mpc}^3$ comoving. 
The limiting magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
$\sim30 $mag in  the  deepest field (XDF). 
The total number of $z=6$ LBG candidates is $940$, most of 
them in the faint end of the LF given the relativeley small survey volume.
The restframe UV magnitudes for these candidates are in the range.
$-22.52\leq M_{1600} \leq -16.77$.
The estimated Schechter parameters:
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
%\citet{Bouwens15} notes that only using few fields of view can yield a
%LF with a deviations from the Schechter shape.

\subsection{Finkelstein et al. 2014}
\citet{Finkelstein14} worked also with HST data.
They used results from the HUDF, CANDELS and GOODS  fields, along with
two of the Hubble Frontier Fields (HFF) of deep parallel  observations
(unlensed fields) near the Abell 2744 and MACS J0416.1-2403  clusters. 
The HFF uses the ACS and the WFC3/IR with the same filters
aforementioned except $z_{850}$. 
The total survey area is around   $\sim300\textrm{arcmin}^2$ with a
total estimated volume of $8\times 10^5$ Mpc$^{-3}$.
There are 706 photometric candidates at redshift 6  defined as the
interval $5.5<z<6.5$. 
The Schechter function parameters estimated for this data set 
are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.

\subsection{Willott et al. 2013}
\citet{Willott13} presented results form the sixth release of the Canada-France-Hawaii 
Telescope Legacy Survey (CFHTLS). 
The observations where performed over four separated fields covering a
total area $\sim 4 \deg^2$ giving a survey volume of $\sim 1 \times
10^7 \textrm{Mpc}^3$, which is over one order of magnitude larger than
the compilations by \citet{Bouwens15} and \citet{Finkelstein14}

They performed otical observations with MegaCam.
Their main selection criteria was that all objects must be brighter
than magnitude $z' = 25.3$. 
The final  number of LBGs founded was 40. 
Moreover, they get spectroscopic confirmation 
for 7 candidates using GMOS spectrograph on the Gemini Telescopes, which 
has a $\ll 5.5$-square arcmin field of view,

%They show incompleteness in the sample due to 
%foreground contamination and the detection algorithm; there is no warranty to 
%have every object brighter than the limit magnitude on the faint
%limit. 
The survey was focused on the most luminous LBGs. 
The full LF at $z=6$ cannot be obtained as in other studies, however
its large volume allows constraints on the bright end.
The LF Schechter parameters are calculated in the magnitud range 
$-20.5 > M_{1350} > -22.5$.

\subsection{McLure et al. 2009}

\citet{McLure09} used data obtained with the 
the United Kingdom Infrared Telescope (UKIRT) in the near-IR imaging
and Subaru Telescope for the optical imaging. 
They covered $2268$ arcmin$^{2}$  for a volume $\sim 3 \times 10^6 \textrm{Mpc}^3$.
The UKIRT was equipped with the WFCAM using $J K$ filters, while Subaru was 
equipped with the Suprime-Cam with the $B V R i' z'$ filters. 
All candidates  where brighter than $z'=26$. 
The UV rest frame magnitude range is 
$-22.4\leq M_{1500} \leq-20.6$. 
The LF was calculated using the maximum 
likelihood estimator of \citet{Schmidt68}. 
Their analysis gave a total number of 
$104$ LBG candidates in the redshift range $5.7\leq z \leq 6.3$. 
They reported the following values for the Schechter function
$\phi^* =(1.8\pm 0.5)\times 10 ^{-3} \textrm{Mpc}^{-3}$, 
$M^*_{1500} = -20.04\pm 0.12$ and $\alpha = -1.71 \pm 0.11$.

@@

The observational datasets were retrieved using
GAVO-DEXTER\footnote{\url{http://dc.zah.uni-heidelberg.de/dexter/ui/ui/custom}}.
